Multi-target detection with application to cryo-electron microscopy

### 2019-02-26 inverse_problems/inverse_problems.tex
Re-arranged Section 6, in particular some titles

\subsection{Proof of Proposition~\ref{prop:poisson}} \label{sec:proof_prop_poisson}

>>>>

\subsection{Autocorrelations in the Poisson model} \label{sec:proof_prop_poisson}

\TODO{Needs a complete rewrite to match the paper, in particular the modified notation and the fact we only work with autocorrelations now (not models).}
